Analytic choices for analyzing multidimensional behavior - Many analysts test hypotheses about human speech.

### 2021-03-24 RR_manuscript/Draft_RR.Rmd
added parker et al. bibtex

Several other recent studies corroborated this analytic flexibility across different disciplines.
Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.
<!-- TODO: Parker et al. (ECO) REFS -->
Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also Parker et al. (accepted) on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

@@

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
<!-- TODO: add LINK to informed consent form -->
All analysts will sign a consent (ethics) document (LINK).
<!-- TODO: add information about what this consent form does -->

<!-- TODO: Parker et al. (ECO) REFS -->
Following Parker et al. [ECO RR], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:

>>>>

Several other recent studies corroborated this analytic flexibility across different disciplines.
Both @dutilh2019 ad @starns2019assessing investigated analysts' choices when inferring theoretical constructs based on the same data set using computational models.

Both studies revealed vastly different modeling strategies, even though scientific conclusions were similar across analysis teams [see also @Parker2020 on analytic flexibility in ecology and @botvinik-nezer2020 on neuroimaging data].
@bastiaansen2020 crowdsourced clinical recommendations based on analyses of an individual patient.
Results suggests that analysts differed substantially regarding decisions related to both the statistical analysis of the data and the theoretical rationale behind interpreting the statistical results.

@@

We will simultaneously recruit volunteers to peer-review the analyses conducted by the other volunteers through the same channels.
Our goal is to recruit a similar number of peer-reviewers and analysts, and to ask each peer reviewer to review a minimum of four analyses.
If we are unable to recruit at least half the number of reviewers as analysis teams, we will ask analysts to serve also as reviewers (after they have completed their analyses).
All analysts and reviewers will share co-authorship on this manuscript and will participate in the collaborative process of producing the final manuscript.
<!-- TODO: add LINK to informed consent form -->
All analysts will sign a consent (ethics) document (LINK).

Following Parker et al. [@Parker2020], we identified a minimal sample size that would provide an estimate of heterogeneity of the effect sizes reported by the analysis teams ($\tau^2$, i.e. the variance $\sigma^2_{\alpha_{\text{t}}}$, see \Cref{s:meta-est}).
In short, the minimal sample size is considered the number of analysis teams needed to allow an estimation of heterogeneity.
We consider a posterior distribution of $\tau^2$, for which the 95% credible interval (CrI) does not include 0 as sufficient.
The probability $Pr$ that a CrI interval does not include 0 is obtained via the *t*-statistic:
